\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-05-15 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	deleted:    manuscript/main.aux 	deleted:    manuscript/main.blg 	modified:   manuscript/main.fdb_latexmk 	deleted:    manuscript/main.fls 	deleted:    manuscript/main.log 	deleted:    manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz

To characterize the real estate brokerage market, we can assume that there are two types of brokerages in the market, where the type $1$ denote the large real estate brokerage that is incorporating the online platform and the offline stores strategies, and the type $2$ denote the small real estate brokerage that only have the offline stores and they should compete with the type $1$ stores and type $2$ stores in the market. Each type of brokerage follows a standard percentage charge by $r_j$ where $j \in \{1, 2\}$ and they can not manipulate the percentage charge in each submarket.

@@

The brokerages have the same positive cost function denoted as $C(\cdot)$ where $\frac{\partial C(\cdot)}{\partial \mathcal{B}_{j}} > 0$ and $\frac{\partial C^2(\cdot)}{\partial \mathcal{B}_{j}^2} > 0$ where $j \in \{1, 2\}$. The intuition is that because of the marginal cost of the platform is $0$, when considering the cost of opening additional stores in the market, the brokerage does not incur that cost into consideration and therefore, the cost function is equal for both types of stores. Moreover, the marginal cost of opening additional stores is increasing, which is consistent with the real estate brokerage market because the more stores the brokerage opens, the administrative cost will increase.

@@

\begin{equation}
  N_{i, j} = L^N_i \times \frac{\mathcal{B}_{i, j}}{\mathcal{B}_{i, 1} + \mathcal{B}_{i, 2}}. \label{eq:naive_prob}
\end{equation}

However, the broad searchers in the market are attracted to the platform by the networking because they are searching for all the communities in the market,

\begin{equation}
  B_i = L^B_i \times \alpha_j \times \frac{\mathcal{B}_{i, j}}{\mathcal{B}_{i, 1} + \mathcal{B}_{i, 2}} \label{eq:broad_prob}
\end{equation}

@@

\begin{equation}
  L_{i, j} = N_{i, j} + B_{i, j} = (L^N_i + L_B \times \beta \times \alpha_j) \times \frac{\mathcal{B}_{i, j}}{\mathcal{B}_{i, 1} + \mathcal{B}_{i, 2}}
   \label{eq:total_prob}
\end{equation}

We can assume there is an exogenous probability of getting the transaction complete by $\tau_{i, j}$ and the revenue for each brokerage $j$ in community $i$ can be calculated by considering the total number of transactions completed, which is the product of the number of customers handled by the brokerage and the probability of transaction completion.

@@

>>>>

To characterize the real estate brokerage market, we can assume that there are $\mathcal{N}$ types of brokerages in the market, where the type $1$ denote the large real estate brokerage that is incorporating the online platform and the offline stores strategies, and the type $2$ to type $\mathcal{N}$ denote the small real estate brokerage that only have the offline stores and they should compete with the type $1$ stores and type $2, \ldots, \mathcal{N}$ stores in the market. Each type of brokerage follows a standard percentage charge by $r_j$ where $j \in \{1, 2, \ldots, \mathcal{N}\}$ and they can not manipulate the percentage charge in each submarket.

@@

The brokerages have the same positive cost function denoted as $C(\cdot)$ where $\frac{\partial C(\cdot)}{\partial \mathcal{B}_{j}} > 0$ and $\frac{\partial C^2(\cdot)}{\partial \mathcal{B}_{j}^2} > 0$ where $j \in \{1, 2, \ldots, \mathcal{N}\}$. The intuition is that because of the marginal cost of the platform is $0$, when considering the cost of opening additional stores in the market, the brokerage does not incur that cost into consideration and therefore, the cost function is equal for both types of stores. Moreover, the marginal cost of opening additional stores is increasing, which is consistent with the real estate brokerage market because the more stores the brokerage opens, the administrative cost will increase.

@@

\begin{equation}
  N_{i, j} = L^N_i \times \frac{\mathcal{B}_{i, j}}{\sum_{j^\prime=1}^{\mathcal{N}}\mathcal{B}_{i, j^\prime}}. \label{eq:naive_prob}
\end{equation}

However, the broad searchers in the market are attracted to the platform by the networking because they are searching for all the communities in the market, and buyers have different preferences for brokerages based on their online presence, reputation and other factors, with private information $\theta_{b, j}$ representing the buyer's preference for brokerage $j$.

\begin{equation}
  B_i = L^B_i \times \alpha_j \times \frac{\mathcal{B}_{i, j} \times \theta_{b, j}}{\sum_{j^\prime=1}^{\mathcal{N}}\mathcal{B}_{i, j^\prime} \times \theta_{b, j^\prime}} \label{eq:broad_prob}
\end{equation}

@@

\begin{equation}
  L_{i, j} = N_{i, j} + B_{i, j} = (L^N_i + L_B \times \beta \times \alpha_j) \times \frac{\mathcal{B}_{i, j} \times \theta_{b, j}}{\sum_{j^\prime=1}^{\mathcal{N}}\mathcal{B}_{i, j^\prime} \times \theta_{b, j^\prime}}
   \label{eq:total_prob}
\end{equation}

We can assume the probability of a successful match between buyers and sellers, which increases with the number of participants on the platform, as $\tau_{i, j} = f(\frac{\mathcal{B}_{i, j}}{\sum_{j^\prime=1}^{\mathcal{N}}\mathcal{B}_{i, j^\prime}})$ and the revenue for each brokerage $j$ in community $i$ can be calculated by considering the total number of transactions completed, which is the product of the number of customers handled by the brokerage and the probability of transaction completion.

@@

% here is my question using rigorous mathematical model and mathematical framework to:

% now formulate the assumption that other store's brokerage are homogenous and the brokerage $1$'s network effect is greater than other bokerage.

% now give me the first proposition that in equilibrium, the number of brokerage $1$'s share in the market is greater than the number of brokerage $1$'s proportion of number of stores. Besides, the brokerage $1$'s optimal choice of broekrage charge is greater than other brokerage

\begin{assumption}[homogenous brokerage]
  The brokerage $1$'s network effect is greater than other brokerages in the market and assume that the small brokerages (Type $2$ to $\mathcal{N}$) are homogenous and they have the same network effect in the market, i.e., $\alpha_2 = \ldots = \alpha_{\mathcal{N}} = \alpha_s$, where $\alpha_s$ is the network effect for small brokerages. We have $\alpah_1 > \alpha_s$.
\end{assumption}

\begin{proposition}[brokerage $1$'s optimal choice]
  In equilibrium, the market share of Brokerage 1 (Type 1) is greater than its proportion of the number of stores, and the optimal brokerage fee charged by Brokerage 1 is higher than that charged by other brokerages. 
\end{proposition}

\begin{proof}
  The total number of customers for Brokerage 1 in community $i$ is given by $L_{i, 1}$ and the total number of stores is $L_{i}$:

  \begin{equation}
    \text{Market Share}_{i, 1} = \frac{L_{i, 1}}{L_i}
  \end{equation}

  Since $\alpha_1 > \alpha_s$ and assuming $\theta_{b, 1} \geq \theta_{b, j}$ and Brokerage 1 will attract a higher proportion of broad searchers $L^B$, resulting in a larger market share. Thus, in equilibrium, the market share of Brokerage 1 is greater than its proportion of the number of stores.

  To maximize the profit, brokerage $1$ will change $r_1$ such that: $\frac{\partial \Pi_{i, 1}}{\partial r_1} = \frac{\partial R_{i, 1}}{\partial r_1} - \frac{\partial C(\mathcal{B}_{i, 1})}{\partial r_{1}} = 0$. Since $\tau_{i, 1}$ and $L_{i, 1}$ are higher for brokerage $1$ due to the stronger network effect, the optimal $r_1$ will be higher compared to the fees charged by other brokerages, $r_j$ for $j \neq 1$.
\end{proof}

In the following proposition, we will derive the total surplus of the model.

Now we derive the cosumer surplus, which is:

% now consider the two-period entry model now consider the case of the first period there is an equilibrium with all other broekrages but in the next period there is an entry of the first brokerage then derive the new equilibrium of the market and conduct the wellfare analysis in this case

\begin{proposition}[two-period entry model]

\end{proposition}
